Clustering Beat-Chroma Patterns\\ in a Large Music Database

### 2010-05-18 Paper/Paper.tex
acknowledgements and authors updated

% Three addresses
% --------------
\threeauthors
  {First author} {Affiliation1 \\ {\tt author1@ismir.edu}}
  {Second author} {\bf Retain these fake authors in\\\bf submission to preserve the formatting}
  {Third author} {Affiliation3 \\ {\tt author3@ismir.edu}}
% what order do we use? Thierry, Ron, Dan?  Dan, Thierry, Ron?

@@

%\small
%\section{Acknowledgements}
%Thierry is NSERC graduate fellow, or some title like that.
%Ron has a grant too.
% Graham for the NMF stuff and numerous discussions.

>>>>

% Three addresses
% --------------
\threeauthors
  {Thierry Bertin-Mahieux} {Columbia University\\ {\tt tb2332@columbia.edu}}
  {Ron Weiss} {New York University \\ {\tt ronw@nyu.edu}}
  {Dan Ellis} {Columbia University \\ {\tt dpwe@ee.columbia.edu}}
% what order do we use? Thierry, Ron, Dan?  Dan, Thierry, Ron?

@@

%\small
\section{Acknowledgements}
Thanks to Graham Grindlay for numerous discussions and helpful comments.
T. Bertin-Mahieux is supported by a NSERC scholarship.
This material is based upon work supported by the IMLS (grant LG-06-08-0073-08).
